Natural selection in the Health and Retirement Study

### 2023-09-19 hrs-selection.qmd
Try out the futureverse...

library(haven)
library(forcats)
library(dplyr, warn.conflicts = FALSE)
library(stringr)
library(purrr)
library(ggplot2)
library(tidyr)
library(santoku, warn.conflicts = FALSE) # masks tidyr::chop
 # masks dotchart:
suppressPackageStartupMessages(library(survey, warn.conflicts = FALSE))

@@

confint_workaround <- function (x) {
  cbind(
    as.numeric(x) - 1.96 * SE(x), 
    as.numeric(x) + 1.96 * SE(x))
}

@@

  form_pgs <- map(pgs, \(x) reformulate(c(x, pcs), response = "rlrs"))
  mod_pgs[[eth]] <- map(form_pgs, 
                        \(x) svyglm_quiet(x, r_eth)
                        )

@@

  form_pgs_edyrs <- map(pgs, \(x) reformulate(c(x, pcs),
                                              response = "raedyrs"))
  mod_pgs_edyrs[[eth]] <- map(form_pgs_edyrs, 
                              \(x) svyglm_quiet(x, r_eth)
                              )

@@

  form_pgs_sibs <- map(pgs, 
                       \(x) reformulate(c(x, pcs), response = "r10sibs"))
  mod_pgs_sibs[[eth]] <- map(form_pgs_sibs,
                             \(x) svyglm_quiet(x, r_parents_eth))

@@

  # the colon interaction estimates the effect separately within each group
  form_pgs_x_ed <- paste0(pgs, ":edu") |>
    map(\(x) reformulate(c(x, "edu", pcs), response = "rlrs"))
  mod_pgs_x_ed[[eth]]  <-
    map(form_pgs_x_ed, 
        \(x) svyglm_quiet(x, r_eth)
        )

@@

  form_pgs_x_inc <- paste0(pgs, ":income_med") |>
    map(\(x) reformulate(c(x, "income_med", pcs), response = "rlrs"))
  mod_pgs_x_inc[[eth]]  <-
    map(form_pgs_x_inc, 
        \(x) svyglm_quiet(x, r_eth)
        )

@@

  form_pgs_x_mar <- paste0(pgs, ":married") |>
    map(\(x) reformulate(c(x, "married", pcs), response = "rlrs"))
  mod_pgs_x_mar[[eth]]  <-
    map(form_pgs_x_mar, 
        \(x) svyglm_quiet(x, r_eth)
        )

@@

  form_pgs_x_agefb <- paste0(pgs, ":agefb") |>
    map(\(x) reformulate(c(x, "agefb", pcs), response = "rlrs"))
  mod_pgs_x_agefb[[eth]]  <-
    map(form_pgs_x_agefb, 
        \(x) svyglm_quiet(x, r_eth)
        )

@@

```{r}
#| label: stat-bootstrap-eth-cor
#| cache: true
#| cache-lazy: false

@@

>>>>

library(haven)
library(forcats)
library(dplyr, warn.conflicts = FALSE)
library(stringr)
library(purrr)
library(ggplot2)
library(tidyr)
library(santoku, warn.conflicts = FALSE) # masks tidyr::chop
library(future)
library(furrr)
 # masks dotchart:
suppressPackageStartupMessages(library(survey, warn.conflicts = FALSE))

plan(multisession, workers = 6)

@@

# workaround failure in confint.svrepdesign
confint_workaround <- function (x) {
  cbind(
    as.numeric(x) - 1.96 * SE(x), 
    as.numeric(x) + 1.96 * SE(x))
}

@@

  form_pgs <- map(pgs, \(x) reformulate(c(x, pcs), response = "rlrs"))
  mod_pgs[[eth]] <- future_map(form_pgs, 
                               \(x) svyglm_quiet(x, r_eth))

@@

  form_pgs_edyrs <- map(pgs, \(x) reformulate(c(x, pcs),
                                              response = "raedyrs"))
  mod_pgs_edyrs[[eth]] <- future_map(form_pgs_edyrs, 
                                     \(x) svyglm_quiet(x, r_eth))

@@

  form_pgs_sibs <- map(pgs, 
                       \(x) reformulate(c(x, pcs), response = "r10sibs"))
  mod_pgs_sibs[[eth]] <- future_map(form_pgs_sibs,
                                    \(x) svyglm_quiet(x, r_parents_eth))

@@

  # the colon interaction estimates the effect separately within each group
  form_pgs_x_ed <- paste0(pgs, ":edu") |>
    map(\(x) reformulate(c(x, "edu", pcs), response = "rlrs"))
  mod_pgs_x_ed[[eth]]  <-
    future_map(form_pgs_x_ed, 
               \(x) svyglm_quiet(x, r_eth))

@@

  form_pgs_x_inc <- paste0(pgs, ":income_med") |>
    map(\(x) reformulate(c(x, "income_med", pcs), response = "rlrs"))
  mod_pgs_x_inc[[eth]]  <-
    future_map(form_pgs_x_inc, 
               \(x) svyglm_quiet(x, r_eth))

@@

  form_pgs_x_mar <- paste0(pgs, ":married") |>
    map(\(x) reformulate(c(x, "married", pcs), response = "rlrs"))
  mod_pgs_x_mar[[eth]]  <-
    future_map(form_pgs_x_mar, 
               \(x) svyglm_quiet(x, r_eth))

@@

  form_pgs_x_agefb <- paste0(pgs, ":agefb") |>
    map(\(x) reformulate(c(x, "agefb", pcs), response = "rlrs"))
  mod_pgs_x_agefb[[eth]]  <-
    future_map(form_pgs_x_agefb, 
               \(x) svyglm_quiet(x, r_eth))

@@

```{r}
#| label: stat-bootstrap-eth-cor
#| cache: true
#| cache-lazy: false
#| eval: false

# I don't mention this below so turning it off for now
# TODO: should I mention it? It's a low correlation.

@@

# use this rather than future_map, to avoid setup costs.
# Not sure it actually does anything :-)
options(survey.multicore = TRUE)
